---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# visTimeEvent

<!-- badges: start -->
<!-- badges: end -->

The goal of visTimeEvent is to quickly generate well-formatted Kaplan-Meier or cumulative incidence curves, with or without competing risks.

## Installation

You can install the development version of visTimeEvent from [GitHub](https://github.com/KGutmair/visTimeEvent) with:

``` r
# install.packages("pak")
pak::pak("KGutmair/visTimeEvent")
```

# Description

This package provides functions for creating Kaplan-Meier and cumulative incidence plots. These functions serve as wrappers for ggsurvfit() and cuminc(), allowing for the quick generation of well-formatted visualizations. Users can choose to display the median time-to-event probability, median cumulative incidence, or event probability at a specific timepoint along with corresponding confidence intervals. When comparing two groups, the plot includes the p-value from the appropriate hypothesis test for assessing differences between them.

Following functions are available:

-   Kaplan-Meier curves:

    -   `km_single`: This function plots the Kaplan-Meier curve for a single group.

    -   `km_grouped`: This function plots the Kaplan-Meier curve stratified by two groups. The p-value from the log-rank or Wilcoxon test is included in the plot.

    -   `km_grouped_weighted`: This function plots weighted Kaplan-Meier curves for two groups, using weights such as those from Propensity Score Inverse Probability of Treatment Weighting (IPTW) or other methods. The p-value from the stratified log-rank test is also displayed.

-   Cumulative incidence curves:

    -   `comp_risk_single`: This function plots the cumulative incidence curves for competing events.

    -   `comp_risk_grouped`: This function Plots cumulative incidence curves for two groups with competing events, showing only the first event. The p-value for comparing the curves is also displayed.





# Example

```{r example}
library(visTimeEvent)
library(dplyr)
library(survival)

test_dat <- survival::pbc
test_dat <- test_dat %>%
  mutate(status_death = ifelse(status == 2, 1, 0),
         status_death = as.integer(status_death),
         time = time/365,
         trt = as.factor(ifelse(trt == 1, "treatment", "placebo")),
         trt_num = ifelse(trt == "treatment", 1, 0),
         status = as.factor(status)) %>%
  filter(!is.na(trt))
```



```{r KM_plot_one_group}
plot_km <- km_single(data = test_dat,
          time = "time",
          event = "status_death",
          title = "Kaplan-Meier curves for one group",
          unit = "years",
          endpoint = "OS",
          colors = "darkblue",
          show_label = "median")
plot_km[[1]]
```

```{r KM_plot_two_groups}
plot_km1<- km_grouped(data = test_dat,
          time = "time",
          event = "status_death",
          group = "trt",
          time_survival = 6,
          test = "wilcoxon",
          title = "Kaplan-Meier curves for two groups",
          unit = "years",
          endpoint = "OS",
          colors = c("darkblue", "darkgreen"),
          show_label = "probability")

plot_km1[[1]]

```


```{r cumulative_incidence_plot_one_group}
plot_cum <- comp_risk_single(data = test_dat,
                 time = "time",
                 event = "status",
                 title = "Competing risk of a single group",
                 unit = "years",
                 colors = c("darkred", "darkblue"),
                 show_label = "probability",
                 time_survival = 8)

plot_cum[[1]]
```
