---
title: "visTimeEvent package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(visTimeEvent)
```

# Description

This package provides functions for creating Kaplan-Meier and cumulative incidence plots. These functions serve as wrappers for ggsurvfit() and cuminc(), allowing for the quick generation of well-formatted visualizations. Users can choose to display the median time-to-event probability, median cumulative incidence, or event probability at a specific timepoint along with corresponding confidence intervals. When comparing two groups, the plot includes the p-value from the appropriate hypothesis test for assessing differences between them.

Following functions are available:

-   Kaplan-Meier curves:

    -   `km_single`: This function plots the Kaplan-Meier curve for a single group.

    -   `km_grouped`: This function plots the Kaplan-Meier curve stratified by two groups. The p-value from the log-rank or Wilcoxon test is included in the plot.

    -   `km_grouped_weighted`: This function plots weighted Kaplan-Meier curves for two groups, using weights such as those from Propensity Score Inverse Probability of Treatment Weighting (IPTW) or other methods. The p-value from the stratified log-rank test is also displayed.

-   Cumulative incidence curves:

    -   `comp_risk_single`: This function plots the cumulative incidence curves for competing events.

    -   `comp_risk_grouped`: This function Plots cumulative incidence curves for two groups with competing events, showing only the first event. The p-value for comparing the curves is also displayed.
  

# Examples

